
\textbf{\large Research \& Development Chemist} \hfill Casual \textbf{Apr 2020--Current}\par
\vspace{1mm}
\textit{Inline Cosmetic Laboratories} \hfill Full-time \textbf{Jul 2015--Apr 2020}\par
\vspace{1mm}
\hfill Beenleigh, QLD, Australia \par
\vspace{1mm}
I design and develop novel cosmetic products for a variety of brands. I transitioned from full-time to casual employment when I commenced my PhD in April 2020.\par
\vspace{2mm}
\textit{Key skills} \par
\begin{itemize}
	\item Independently gathering the information required to create and deliver innovative products on-time and within-budget.
	\item Managing multiple projects with different timelines simultaneously, in a fast-paced and consumer-focussed environment.
	\item Taking ownership of projects across their entire lifecycle: from conceptualisation to launch, and continual quality monitoring.
	\item Liaising with key project stakeholders to achieve a common goal, including colleagues, customers, and suppliers.
    \item Mentoring and training junior staff and conducting annual performance reviews.
	% \item Preparing documentation for nationally-recognised accreditation bodies, including Australian Certified Organic.
	% \item Trouble-shooting technical issues as they arise.
	% \item Researching relevant national and international legislation to deliver compliant consumer products.
	% \item Technical review of conference presentations.
	% \item Resilient and seeking new challenges.
	% \item Conducting annual performance reviews of current employees and interviewing potential employees.
\end{itemize}\par
\vspace{2mm}
\textit{Achievements} \par
\begin{itemize}
	\item MForHer award (2022), Merck Life Sciences. \textit{I received this award celebrating women in science due to my passion for research.}
\end{itemize}\par